What is a Selection Coefficient?

### 2021-12-16 graphs_newt_snakes/What_is_sel_coef.Rmd
I got the small area cov to be caculated. I need to figure out a better way to color it and save it (print it out in txt)
writing more about what i want to do in my selection experiment (the rmarkdown). working on improving the color for little beta in the newt snake 1on1. I am setting up the selection experiment for the no space slim. in nospaceslim1on1 i am trying out the writeFile funtion rating 10/10
I started to make graph/animations for the selection experiments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

This Is how I would like one of the phenotypes to look if there was an advantage. I was trying to use Msprime to get this type of distribution, but it wasn't working.

@@

Heritability and genetic correlation page 54

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(gganimate)
library(gifski)
library(gapminder)
```

@@

This is how I would like one of the phenotypes to look if there was an advantage. I was trying to use Msprime to get this type of distribution, but it wasn't working.

@@

Heritability and genetic correlation page 54 might be more info in ch 9

## NoSpace Selection Experiment

Peter and I talked through a selection experiment in the nospace slimulation. We decided that newts' toxicity would be able to mutate and coevolve with to the snakes resistance (snakes phenotype is set to a value and unable to mutate). I picked parameters that would (hopefully) cause the newts toxicity phenotype to evolve quickly. I also tried increasing interaction rate and moving the snake resistant phenotype further or closer to the newt mean phenotype.

I want to look at the newts' phenotype, fitness, and its ability to survive (based on phenotype) throughout the generations. Sometimes I get extreme newt phenotypes if the mutation rate is too high. In every simulation where newts became more toxic than snakes there was some competition between snakes and newts where snakes were eating any newt. Then newts and snakes were killing each other. Finally, newts were killing any snake that they met. The transition between newts being eaten by snakes to newts and snakes were killing each other took more time (generations) then when newt became more toxic than snakes.

```{r, data}

files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
file <- read.table(files[1], header = TRUE)
```

```{r, pheno dist graph, warning = F}
#animation.hook="gifski"

hist(file$phenotype[file$gen==1], col="darkred",xlim = c(0, 3), main = "Newt Phenotypes Distribution for 1st Gen", xlab = "Phenotype")
#xlim = c(1, 6)

p1<-ggplot(file, aes(phenotype)) + 
  geom_histogram(col = "darkred", fill = "darkred", binwidth=30)+ 
  theme_bw()+
  scale_y_log10()+
  xlim(-1, 1000) +
  # gganimate specific bits:
labs(title = 'Newt Phenotype Dist. Generation: {frame_time}', x = 'Phenotype', y = 'Count') +
  transition_time(gen) +
  ease_aes('linear')
animate(p1, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1.gif")
```

```{r, pheno fit graph, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-"extra stuff"
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2.gif")
```

```{r, pheno fit graph log, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-"extra stuff"
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    scale_x_log10()+
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 25, fps = 30, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2log.gif")
